A Study on Penguins: A Minimal Reproducible Example

### 2024-05-16 01_Example/Manuscript.qmd
updated minimal exmple

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Kan Garoo"
    affiliation: "University of Melbourne"
    email: "kangaroo@email.com"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  quarto::apa_document
bibliography: Bibliography.bib
---

@@

# Call descriptive table with the vtable package
vtable::sumtable(data_clean, group = "species")
```

>>>>

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Josephine Zerna"
    email: "josephine.zerna@tu-dresden.de"
    orcid: 0000-0003-2892-884X
    roles:
      - conceptualization
      - writing
    affiliations:
      - id: id1
        name: "Technische Universität Dresden"
        group: Chair of Differential and Personality Psychology
        department: Faculty of Psychology
        city: Dresden
        postal-code: 01069
  - name: "Christoph Scheffel"
    affiliation: 
      - id: id1
    email: "christoph_scheffel@tu-dresden.de"
    orcid: 0000-0001-5963-9229
    corresponding: true
    roles:
      - project administration
      - methodology
date: "`r format(Sys.Date(), '%B %d, %Y')`"
abstract: "This document is a minimal, reproducible manuscript using the penguins data set as an example."
keywords: [penguins, reproducibility, minimal, example]
floatsintext: false
bibliography: Bibliography.bib
format:
  #apaquarto-docx: default
  #apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    keep-tex: true

---

@@

# Call descriptive table with the vtable package
vtable::sumtable(data_clean, group = "species")

### 2024-05-16 01_Example/Manuscript.tex
updated minimal exmple

\author{Kan Garoo}

\affiliation{
{University of Melbourne}}

\leftheader{Garoo}

\date{2024-04-29}

%

\authornote{
\par{ }
\par{       }
\par{Correspondence concerning this article should be addressed to }
}

>>>>

\authorsnames{Josephine Zerna,Christoph Scheffel}

\authorsaffiliations{
{Faculty of Psychology, Technische Universität Dresden},{}}

\leftheader{Zerna and Scheffel}

\date{Invalid Date}

\abstract{This document is a minimal, reproducible manuscript using the
penguins data set as an example.}
% 
\keywords{penguins, reproducibility, minimal, example}

\authornote{\par{\addORCIDlink{Josephine
Zerna}{0000-0003-2892-884X}}\par{\addORCIDlink{Christoph
Scheffel}{0000-0001-5963-9229}}
\par{ }
\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Josephine
Zerna:   conceptualization, writing; Christoph Scheffel:   project
administration, methodology}
\par{Correspondence concerning this article should be addressed
to Christoph Scheffel, Email: christoph\_scheffel@tu-dresden.de}
}
